article title

### 2022-07-20 article.tex
Refactor tables

@@

\begin{table}[H]
\begin{flushleft}
\begin{tabular}{ccc}
\toprule
$A$      & $B$ & $ A \land B$ \\
\midrule
T        & T   & T \\
T        & F   & F \\
F        & T   & F \\
F        & F   & F \\
\bottomrule
\end{tabular}
\label{tab:boolean_truth_table}
\caption{Boolean truth table}
\end{flushleft}
\end{table}

>>>>

\subsection{Simple table}
\label{sec:simple_table}`

@@

\subsection{Multirow table}
\label{sec:multirow_table}`
\begin{table}[H]
\footnotesize
\centering
\begin{tabular}{llll}
\toprule
                                           & \textbf{Process requirement}            & \textbf{Sampling}                        & \textbf{Comments} \\
\midrule
\multirow[t]{4}{*}{$C_\text{pk}$}          & - Stable and predictable variation      & - Rational                               & - Possible cost to increasing $C_\text{pk}$ \\
                                           & - Normal distribution                   & - Representative of process              & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$P_\text{pk}$}          & - Stable and predictable variation      & - Random                                 & - Possible cost to increasing ppk \\
                                           & - Normal distribution                   & - Sufficiently large, representative     & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & - Easiest formulae to explain \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$C_\text{pm}$}          & - Stable and predictable variation      & - Same as $C_\text{pk}$ or $P_\text{pk}$ & - $C_\text{pm}$ penalizes for being off-target \\
                                           & - Normal distribution                   &                                          & - Wide confidence interval \\
                                           & - Need at least one specification limit &                                          & - Most difficult formulae to explain \\
                                           & - Need specification target             &                                          & \\
\bottomrule
\end{tabular}
\caption{Comparison of capability indices}
\label{tab:comparison_capability_indices}
\end{table}
